### 2013-07-24 doc/asplos14/method.tex

\vspace{0.5ex}
\noindent{\bf Breadth-first-search (BFS):} This is the primary kernel for the
Graph500 benchmark and is what currently determines the ranking of machines on
the Graph500 list~\cite{graph500list}. As a whole, the Graph500 benchmark
suite is designed to bring the focus of system design on data-intensive
workloads, particularly large-scale graph analysis problems, that are
important among cybersecurity, informatics, and network-understanding
workloads. The BFS benchmark builds a search tree containing parent nodes for
each traversed vertex during the search. While this is a relatively simple
problem to solve, it exercises the random-access and fine-grained
synchronization capabilities of a system as well as being a primitive in many
other graph algorithms. Performance is measured in \emph{traversed edges per
second\/} (TEPS), where the number of edges is the edges making up the
generated BFS tree. With some modifications to the XMT reference version of Graph500 BFS,
the XMT compiler can be made to recognize and apply a Manhattan loop collapse, exposing enough parallelism to allow it to scale out to 64 nodes for the problem scales we show.
We do not employ algorithmic improvements for any of these versions, though there are
many~\cite{Beamer:Graph500,Yoo:FixedPointGraph500}. \Grappa can be expected to benefit the same as MPI due to decreased communication.

@@

\vspace{0.5ex}
\noindent{\bf PageRank:} This is a common centrality metric for
graphs. Computing PageRank is an iterative algorithm with a common
pattern of gather, apply, and scatter on the rank of vertex. The algorithm
is often implemented by sparse linear algebra libraries, with the main
kernel being the sparse matrix dense vector multiply. For the multiply
step, \Grappa parallelizes over the rows and parallelizes each dot
product. PageRank has the fortunate property that the accumulation
function over the in-edges is associative and commutative, so they can
be processed in any order or in parallel. Rather than the programmer writing the
parallel dot product as local accumulations with a final all-reduce
step, we simply send streaming increments to each element of the final
vector. We compare PageRank to published results for the Trilinos linear algebra library implemented in MPI, and multithreaded PageRank for the XMT~\cite{MTGL:pagerank}.
For \Grappa, we run on a scale 29 graph using the Graph500 generator.

>>>>

\vspace{0.5ex}
\noindent{\bf Breadth-first-search (BFS):} This is the primary kernel for the
Graph500 benchmark and is what currently determines the ranking of machines on
the Graph500 list~\cite{graph500list}. As a whole, the Graph500 benchmark
suite is designed to bring the focus of system design on data-intensive
workloads, particularly large-scale graph analysis problems, that are
important among cybersecurity, informatics, and network-understanding
workloads. The BFS benchmark builds a search tree containing parent nodes for
each traversed vertex during the search. While this is a relatively simple
problem to solve, it exercises the random-access and fine-grained
synchronization capabilities of a system as well as being a primitive in many
other graph algorithms. Performance is measured in \emph{traversed edges per
second\/} (TEPS), where the number of edges is the edges making up the
generated BFS tree. With some modifications to the XMT reference version of Graph500 BFS,
the XMT compiler can be made to recognize and apply a Manhattan loop collapse, exposing enough parallelism to allow it to scale out to 64 nodes for the problem scales we show.
In order to make comparison easier, we do not employ algorithmic improvements for any of these versions, though there are
many~\cite{Beamer:Graph500,Yoo:FixedPointGraph500}. \Grappa can be expected to benefit the same as MPI due to decreased communication.

@@

\vspace{0.5ex}
\noindent{\bf PageRank:} This is a common centrality metric for
graphs. Computing PageRank is an iterative algorithm with a common
pattern of gather, apply, and scatter on the rank of vertex. The algorithm
is often implemented by sparse linear algebra libraries, with the main
kernel being the sparse matrix dense vector multiply. For the multiply
step, \Grappa parallelizes over the rows and parallelizes each dot
product. PageRank has the fortunate property that the accumulation
function over the in-edges is associative and commutative, so they can
be processed in any order or in parallel. Rather than the programmer writing the
parallel dot product as local accumulations with a final all-reduce
step, we simply send streaming increments to each element of the final
vector. We compare PageRank to published results for the Trilinos linear algebra library implemented in MPI~\cite{Plimpton:2011:MML:2286659.2286704},
 and multithreaded PageRank for the XMT~\cite{MTGL:pagerank}.
For \Grappa, we run on a scale 29 graph using the Graph500 generator.
